### 2018-08-28 case_for_support.tex
Edited case for support

  \vspace{3mm}
  \noindent
  {\large \bf 1.1 Background: Using astronomy data to train Thai data scientists}

@@

  Facilitated by STFC funding via the Newton and GCRF programs our team of educators and researchers are developing a highly effective data science training programme for Thai students. As part of this programme, students work with external industries and organisations to gain first-hand experience in using data science to solve real-world problems. The first students involved in our training programme developed novel machine learning-based technologies to identify rare true positive sources within astronomy datasets which contained a much larger (i.e., by a factor of $>1000$) samples of false positives; an example of a heavily imbalanced dataset that off-the-shelf machine learning algorithms struggle to deal with.

  events within astronomy

  As a consequence of STFC funding (via the GCRF and Newton programs) our team of educators and researchers have been

  Since February, 2017, our team of educators and researchers from multiple disciplines and institutions have been

  However, Thai data scientists and their students typically lack access to very large amounts of digital data, restricting their training in ``Big Data'' science that is so crucial for the development of modern economies. To address this problem, we successfully applied for Newton funding (12-month project starting February, 2017) to give the Thai data scientists in our team research experience of working with large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO). GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}. This large, constantly-updated dataset has given our research team the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries.

  \vspace{2mm}
  \noindent
  The primary {\it research} goals of our Newton project were to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO. Our research has led to some novel solutions. For the database component we are developing a hybrid system that combines the structure of a relational database (such at that used by SDSS) with the flexibility of a non-relational database (which are popular within tech. industries). For the ML component, we are developing a new two-stage categorisation algorithm which uses unsupervised ML algorithms to quickly remove obvious artefacts from our data before passing more ambiguous cases to a supervised ML algorithm. Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise involved in the proposed GCRF project has originated from work associated with STFC's core Science Programme.

@@

  \noindent
  At present, the impact of our Newton project is limited to the people directly involved in the project (i.e., Thai and UK astronomers, Thai data scientists and their students), whereas our long-term ambition has always been to broaden the impact of our research to develop the wider Thai economy. In this regard the goal of this GCRF project is to use the technology and skills we have developed to increase the productivity of Thai businesses and organisations. To do this effectively, our team needs to first gain experience of working with such external parties to research how best to adapt our technologies and expertise to their data handling and analysis needs.

  \vspace{2mm}
  \noindent
  For this partnership-building project, we request funds to research how our data archiving and analysis techniques can be adapted to meet the needs of five pre-identified Thai businesses and organisations (hereafter, ``external partners''; see Table 1). All our external partners are based in areas local to the Thai co-Is and have already agreed to work with us throughout the 12-month project (see Letters of Support). At this ``capacity building'' stage, we prefer to limit the number of external partners as it ensures that all parties have a thorough understanding of the goals and expectations of the project from the outset. In addition to our research goals, our aim is to learn lessons and define commonalities of approach that can be applied when we expand the project to work with larger numbers of external partners. Our ambition is to apply for follow-on GCRF funding to support this expansion.

>>>>

  \vspace{3mm}
  \noindent
  {\large \bf 1.1 Background}

@@

  Facilitated by STFC funding via the Newton and GCRF programs (details below) our team of educators and researchers are developing a highly effective data science training programme for Thai students. Within this programme, students work with external research organisations and businesses to gain first-hand experience of using data science to solve real-world problems. To date, this programme has been highly productive, as evidenced by:
  \begin{itemize}
    \item two students presenting peer-reviewed proceedings at three international conferences (one of whom was awarded a ``Best Presentation'' prize);
    \item the publication of five peer-reviewed journal articles or conference proceedings;
    \item successfull collaborations with five external business at the regional level;
    \item keen interest from five national businesses to join our collaboration.
  \end{itemize}
  By building on these sucesses and expanding our external partnerships to a national level, the next phase of our project will establish MFU as a hub for data science research and training within northern Thailand. This will enable future students, businesses and organisations to benefit indefinitely from STFC's present investment.

  The collaboration between the PIs (based at Sheffield and MFU) started in February, 2017, with a 12-month Newton-funded project in which Thai data scientists in our team worked with Thai graduate students to develop Machine Learning (ML)-based algorithms to analyse the large amounts of astronomical data generated by the Gravitational-Wave Optical Transient Observatory (GOTO). GOTO surveys the full observable night sky every two weeks, delivering data on roughly seven million astronomical sources {\it every night}. This large, constantly-updated dataset gave the students involved in that first phase the opportunity to develop the skills and techniques needed to handle and analyse the kinds of Big Data generated by many of today's industries. Following this first phase of the project, we were awarded a further two years' of Newton funding from February 2018 to continue our work with GOTO.

  The primary {\it research} goals of our ongoing Newton project are to: (a) develop a database that is capable of storing large amounts of data that is updated on a daily basis and (b) develop fully-automated Machine-Learning (ML) algorithms capable of quickly and robustly categorising sources detected by GOTO. Our research has led to some novel solutions. For the database component we are developing a hybrid system that combines the structure of a relational database (such at that used by SDSS) with the flexibility of a non-relational database (which are popular within tech. industries). For the ML component, we are developing a new two-stage categorisation algorithm which uses unsupervised ML algorithms to quickly remove obvious artefacts from our data before passing more ambiguous cases to a supervised ML algorithm. Since both goals are to address challenges associated with archiving and analysing large amounts of astronomical data, the science, technology and expertise involved in the proposed GCRF project has originated from work associated with STFC's core Science Programme.

@@

  \noindent
  During the first phase of our Newton-funded project, it became clear that the technologies we are developing and the training we are providing would be of great use to a broad range of organisations and businesses within Thailand. With this in mind, we successfully applied to STFC's 2017 GCRF funding call to fund research into how we could adapt the technology and training we have developed to increase the productivity of Thai businesses and organisations. Through this project, our researchers and students have gained experience of working with five such external partners, and have been praised for their achievements so far (see support letter from Thanapiriya).

  \vspace{2mm}
  \noindent
  Our work funded through the round of GCRF funding has demonstrated our ability to successfully collaborate with external organisations. Our current external partners have a regional, as opposed to national or international, presence. While working with such small-to-medium size partners has proven beneficial in terms of our developing good working relationships, our ultimate goal is to also work with partners with a national presence within Thailand. Doing so will provide MFU with the exposure needed to become self-sustaining in terms of attracting a broad variety of external partners to work with our team and their students.

  For this capacity-building project, we request funds to expand upon our first GCRF-funded project to work with four further external partners, each of which have a more national presence than the partners involved with the first phase. We also request funding to continue our collaboration with Thanapiriya. All our external partners have already agreed to work with us throughout the 24-month project (see Letters of Support). At the end of the first 12 months, however, we plan to hold a networking event to attract other external partners.
